---
title: "Lab8"
author: "Yutian Fang"
date: "11/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Load packages
library(here)
library(tidyverse)
library(corrplot)
library(stargazer)
library(broom)
library(modelsummary)
```

```{r}
homes <- read.csv(here("slo_homes.csv"))
```

A little bit of cleaninng:
Make subset called home_sub that only contains observations(row) where the city is:
- San Luis Obispo
- Arroyo Grande
- Atascadero
- Santa Maria Orcutt

```{r}
home_sub <- homes %>%
  filter(City %in% c("San Luis Obispo", "Arroyo Grande", "Atascadero", "Santa Maria-Orcutt"))
```

## Do a little exploring of our data

Summary statistics (home price, based on city and sale status):

summary table show mean and standard deviation of home price, grouped by city and sale status
```{r, include = FALSE, eval = FALSE}
home_sub %>%
  group_by(City, Status) %>%
  summarize(mean_price = mean(Price, na.rm = TRUE),
            sd_price = sd(Price, na.rm = TRUE))

# Actually I don't even want to run this code: eval = FALSE
ggplot(data = home_sub, aes(x = Price)) + 
  geom_density(aes(color = City, fill = City), alpha = 0.3) +
  scale_x_continuous(limits = c(0,3e6))

```

Explore the relationship (visual data exploration) between square footage and home price.
Change the point COLOR by City, and the point shape by sale status

```{r}
ggplot(data = home_sub, aes(x = SqFt, y = Price)) +
  geom_point(aes(color = City, shape = Status)) +
  geom_smooth(method = "lm")
  
```

## Model the relationship between price and other variables 

```{r}
homes_lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + PricePerSqFt + Status, data = home_sub)

# Make a subst that only conatins the quantitative variables

home_quant <- home_sub %>%
  select(Price:PricePerSqFt)

homes_cor <- cor(home_quant)
homes_cor

corrplot(homes_cor, method = 'ellipse')

#Run Diagnostic plot
plot(homes_lm1)

```

Try another model (homes_lm2) where we simplify this a bit:

- City
- SqFt
- Status

```{r}
homes_lm2 <- lm(Price ~ City + SqFt + Status, data = home_sub)

homes_lm2

plot(homes_lm2)
```

Find the AIC value of each model:lower AIC value implies better balance between model fit and model complexity
```{r}
AIC(homes_lm1)
AIC(homes_lm2)
```

Try another permutation of this model that you think make sense, check out & compare the model fit, outputs and AIC values

Use `modelsummary` to show model outputs side-by-side

If you use modelsummary to return model outputs of multiple models, it wants you to feed it to it as a list
```{r}
modelsummary(list(homes_lm1, homes_lm2))
```

## Start making predictions with this model

Use `broom::augment()`

```{r}
homes_predicted <- augment(homes_lm1)
```

Use the `predict()` function to try out your model on new scenarios that you create
